Model

### 2019-08-30 stats/kids_basic_me.Rmd
add model runs with random intercept for individuals

aoa_ratings <- aoa_ratings_all %>%
  filter(Word %in% d_raw$familiar )%>%
  mutate(mean_aoa = as.numeric(Rating.Mean),
         familiar = Word)%>%
  select(familiar,mean_aoa)
```

@@

ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(width = 0, height = 0.05, alpha = .6)+
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(~familiar)+
  #ggtitle("Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")+
  scale_fill_viridis_d(name = "familiar object")

>>>>

aoa_ratings <- aoa_ratings_all %>%
  filter(Word %in% d$familiar )%>%
  mutate(mean_aoa = as.numeric(Rating.Mean),
         familiar = Word)%>%
  select(familiar,mean_aoa)
```

@@

ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(width = 0, height = 0.05, alpha = .6)+
  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
  geom_smooth(method = "loess", se = F, alpha = .5)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(~familiar)+
  #ggtitle("Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")+
  scale_fill_viridis_d(name = "familiar object")

### 2019-08-30 stats/model.Rmd
add model runs with random intercept for individuals

  var speakerOptimalityParameters = {
    intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
    slope: uniformDrift({a: 0, b: 2, width: 0.5})
  }

@@

  var itemVariability = {
    intercept: uniformDrift({a: 0, b: 1, width: 0.2}),
    slope: uniformDrift({a: 0, b: 1, width: 0.2})
  }

@@

      var itemLineParameters = {
        intercept: gaussianDrift({
          mu: globalLineParameters.intercept, 
          sigma: itemVariability.intercept, 
          width: 0.5
        }),
        slope: Math.pow(gaussianDrift({
          mu: globalLineParameters.slope, 
          sigma: itemVariability.slope, 
          width: 0.5
        }), 2)
      }

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 10,
  cores = 10,
  inference_opts = list(method = "incrementalMH",
                        samples = 4000,
                        burn = 2000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 500)
)

# load this for model parameters with so_slope (0:2)
sem_know_model <- readRDS("../saves/sem_know_new_model.rds")

# # load this for model parameters with wider prior on so_slope (0:3)
# sem_know_model <- readRDS("../saves/sem_know_new_model_2.rds")

# # load this for model parameters with wider prior on so_slope (0:3) (second run)
# sem_know_model <- readRDS("../saves/sem_know_new_model_2_2.rds")%>%
#   filter(Chain != 2)

# # load this for model parameters with even wider prior on so_slope (0:4)
# sem_know_model <- readRDS("../saves/sem_know_new_model_3.rds")

# # load this for model parameters with wider prior on so_slope (0:4), so_int, as well as on global paramters of semantic knowledge
sem_know_model <- readRDS("../saves/sem_know_new_model_4.rds")%>%
  filter(Chain !=9)

#saveRDS(sem_know_model, "../saves/sem_know_new_model_4.rds")

@@

global_sigma<- sem_know_model %>%
  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
  filter(parameter == "parameter", type == "sigma")%>%
    separate(value, into = c("sigma_int", "sigma_slope"),sep = ", ")%>%
    mutate(sigma_int = as.numeric(str_remove_all(sigma_int, "[(c]")),
         sigma_slope = as.numeric(str_remove(sigma_slope, "[)]")))%>%
    gather(parameter, value, sigma_int, sigma_slope)

@@

```{r}
ggplot(item_params, aes(x = value, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter~item, scales = 'free')+
  theme_few()
```

@@

ggplot(global_params, aes(x = value, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter~token, scales = 'free')+
  theme_few()
```

```{r}
ggplot(global_sigma, aes(x = value, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Sigma")+
  facet_grid(~parameter, scales = 'free')+
  theme_few()
```

@@

```{r}
ggsave("../graphs/combination_model_data_by_item.pdf", width = 8, height = 3, scale = 1.5)
```

```{r}
binnned_data <- data_comb%>%
  group_by(subage, alignment, item)%>%
  summarize(k = sum(correct), n = n())%>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         data_mean = (a-1)/(a+b-2),
         data_ci_lower  = qbeta(.025, a, b),
         data_ci_upper = qbeta(.975, a, b),
         subage = factor(subage))%>%
  select(-a,-b,-n,-k)

@@

ggplot(data = cor_plot,aes(x = model_mean, y = data_mean, col = item)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
  geom_point(size = 2,  stroke = 1)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  #ggtitle("3-year-olds")+
  facet_grid(~subage)+
  theme_few() + 
  scale_colour_viridis_d(name ="Item")
```

@@

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  cores = 1,
  inference_opts = list(method = "incrementalMH",
                        samples = 5,
                        burn = 1,
                        verbose = T,
                        lag = 1,
                        verboseLag = 1)
)

>>>>

  var speakerOptimalityParameters = {
    intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
    slope: uniformDrift({a: 0, b: 4, width: 0.5})
  }

@@

  var itemVariability = {
    intercept: uniformDrift({a: 0, b: 2, width: 0.2}),
    slope: uniformDrift({a: 0, b: 1, width: 0.2})
  }

@@

      var itemLineParameters = {
        intercept: gaussianDrift({
          mu: globalLineParameters.intercept, 
          sigma: itemVariability.intercept, 
          width: 0.5
        }),
        slope: gaussianDrift({
          mu: globalLineParameters.slope, 
          sigma: itemVariability.slope, 
          width: 0.5
        })
      }

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "incrementalMH",
                        samples = 4000,
                        burn = 2000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 1000)
)

# Model runs

```{r}
# load this for model parameters with so_slope (0:2)
#sem_know_model <- readRDS("../saves/sem_know_new_model.rds")

# load this for model parameters with wider so_slope (0:4) and wider sigma on sem_int
#sem_know_model <- readRDS("../saves/sem_know_model_wide_sig.rds")

# load this for model parameters with wider so_slope (0:4) and wider sigma on sem_int and forced positive slope for semantic knowledge
#sem_know_model <- readRDS("../saves/sem_know_model_pos_slope.rds")

# load this for model parameters with wider so_slope (0:4) and wider sigma on sem_int and with random intercepts for subjects
#sem_know_model <- readRDS("../saves/sem_know_model_wide_sig_ind.rds")

# load this for model parameters with wider so_slope (0:4) and wider sigma on sem_int, forced positive slope for semantic knowledge and with random intercepts for subjects
sem_know_model <- readRDS("../saves/sem_know_model_wide_sig_pos_slope_ind.rds")

#saveRDS(sem_know_model, "../saves/sem_know_model_wide_sig_ind.rds")

@@

global_sigma<- sem_know_model %>%
  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
  filter(parameter == "parameter", type == "sigma", token != "global_subject_sigmas")%>%
    separate(value, into = c("sigma_int", "sigma_slope"),sep = ", ")%>%
    mutate(sigma_int = as.numeric(str_remove_all(sigma_int, "[(c]")),
         sigma_slope = as.numeric(str_remove(sigma_slope, "[)]")))%>%
    gather(parameter, value, sigma_int, sigma_slope)

subj_sigma<- sem_know_model %>%
  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
  filter(parameter == "parameter", token == "global_subject_sigmas")%>%
  separate(value, into = c("na", "sigma"),sep = ", ")%>%
  select(-na)%>%
  mutate(sigma = as.numeric(str_remove(sigma, "[)]")))

subject_params<- sem_know_model %>%
  separate(Parameter, into = c("parameter", "type","id"), sep = ",")%>%
  filter(parameter == "parameter", type == "subj_intercept")%>%
  separate(value, into = c("na", "int"),sep = ", ")%>%
  select(-na)%>%
  mutate(int = as.numeric(str_remove(int, "[)]")))

@@

```{r}
plot_item_params <- ggplot(item_params, aes(x = value, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter~item, scales = 'free')+
  theme_few()

plot_item_params
```

@@

plot_global_params <- ggplot(global_params, aes(x = value, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter~token, scales = 'free')+
  theme_few()

plot_global_params
```
```{r}
plot_global_sigma <- ggplot(global_sigma, aes(x = value, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Sigma")+
  facet_grid(~parameter, scales = 'free')+
  theme_few()

plot_global_sigma
```

```{r}
plotg_subj_sigma <- ggplot(subj_sigma, aes(x = sigma, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Subject Sigma")+
  theme_few()

plotg_subj_sigma
```

select_id <- me_model_data %>%
  filter(age < 1.3,
         age >1)%>%
  group_by(age,subid)%>%
  summarise(mean = mean(correct))%>%
  mutate(id = subid)

subject_params <- subject_params %>%
  left_join(select_id)%>%
  filter(mean != "NA")%>%
  ungroup()

ggplot(subject_params, aes(x = int, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  geom_vline(aes(xintercept = age), size = 1.5)+
  #geom_vline(aes(xintercept = mean), size = 1.5, col = "red")+
  facet_grid(id+ round(mean,2)~.)+
  xlab("Subject Intercept")+
  theme_few()

ggsave("../graphs/subj_intercept.pdf", width = 5, height = 8, scale = 1.5)

@@

```{r}
ggsave("../graphs/combination_model_data_by_item.pdf", width = 8, height = 3, scale = 1.5)
```
# Correlate model predictions and data 
```{r}
binnned_data <- data_comb%>%
  group_by(subage, alignment, item)%>%
  summarize(k = sum(correct), n = n())%>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         data_mean = (a-1)/(a+b-2),
         data_ci_lower  = qbeta(.025, a, b),
         data_ci_upper = qbeta(.975, a, b),
         subage = factor(subage))%>%
  select(-a,-b,-n,-k)

@@

cor_plot_age <- ggplot(data = cor_plot,aes(x = model_mean, y = data_mean, col = item)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
  geom_point(size = 2,  stroke = 1)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(~subage)+
  theme_few() + 
  scale_colour_viridis_d(name ="Item")
```

@@

```{r}
ggarrange(
plot_item_params,plotg_subj_sigma,
plot_global_params,plot_subject_params,
cor_plot_age, plot_global_sigma,
ncol = 2, nrow = 3, common.legend = T, widths = c(1.7,1))

ggsave("../graphs/overview_wide_slope_wide_sigma_pos_slope_ind.png", width = 12, height = 10, scale = 1.2)

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 8,
  cores = 8,
  inference_opts = list(method = "incrementalMH",
                        samples = 4000,
                        burn = 2000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 1000)
)

saveRDS(sem_know_model, "../saves/sem_know_model_wide_sig_pos_slope_ind.rds")
